Network packet generation for Artificial Intelligence\\

### 2020-02-27 paper1/paper1.tex
Added a table for better clarity

>>>>

\smallskip To provide better clarity, the individual attack classes, including some examples, are listed again in the following table:

\begin{table}[htbp]
\caption{Different attack classes and examples \cite{b2}} 
\centering
\begin{tabular}{ | c | c | }
\hline
Type of attack & Example(s) \\
\hline
Virus & File Infector, Macro Virus \\
Worm & Mass-Mailing Worm, Network-Aware Worm \\
Trojan & Logic Bomb \\
Buffer overflow & Stack Buffer Overflow, Heap Overflow \\
Denial of Service Attack & Host Based, Network Based, Distributed \\
Network-Based Attack & Spoofing,  Web Application Attacks \\
Physical Attack & Basic attacks \\
Password Attack & Dictionary Attack, Brute Force \\
Information Gathering &	Sniffing, Mapping, Security Scanning \\
\hline
\end{tabular}
\label{table:attack-types}
\end{table}
